---
title: "Overview of Project"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, error=FALSE, warning=FALSE)
require(tmap)
require(sf)
require(rpgcolorsr)
tmap_mode("view")
```

Project 24-29 would add new fixed route bus service between the Clarksburg Outlets and Bethesda Metro Station (South Entrance) in Montgomery County, MD.

**Figure 1. Proposed Montgomery County Service**

```{r route overview, out.width = "100%"}

route_file <- "K:/Models/MDOT_MMA/Chapter30_Scoring/Ch30_2023/GTFS/New_Project_Feeds/flash_brt_2023/shapes/rpg_shape.shp"
stops_file <- "K:/Models/MDOT_MMA/Chapter30_Scoring/Ch30_2023/GTFS/New_Project_Feeds/flash_brt_2023/shapes/rpg_stops.shp"

routes <- st_read(route_file, 
                  quiet = TRUE) %>% 
  st_transform(2248)

stops <- st_read(stops_file, 
                 quiet = TRUE) %>% 
  st_transform(2248)

pal <- rpg_color_pal("rpg_colors")(4)

tm_shape(routes) +
tm_lines("surface", palette = pal, lwd = 3,
         title.col = "Service Type") +
tm_shape(stops) +
tm_dots(col = "#8400a8", id = "Name", 
        popup.vars = "stop_name", 
        labels = "Name", size = 0.1) +
tm_basemap ("Esri.WorldGrayCanvas")

```

**Report Table of Contents**

-   [Overview](index.html)
-   [Coding Assumptions](coding-assumptions.html)
-   [Network Review Results](network-review-results.html)
-   [Reasonableness of Results](reasonableness-of-results.html)
-   [Mapping and Findings](mapping-and-findings.html)
