---
title: "Reasonableness of Results"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

require(sf)
require(tmap)
require(rmapshaper)
require(dplyr)
require(kableExtra)
require(readr)
require(tidyr)
require(rpgcolorsr)
require(classInt)
require(tigris)
library(nngeo)
require(janitor)
options(scipen=999)

```

```{r read in stops}

stops_file <- "K:/Models/MDOT_MMA/Chapter30_Scoring/Ch30_2023/GTFS/New_Project_Feeds/flash_brt_2023/shapes/rpg_stops.shp"

stops <- st_read(stops_file, 
                 quiet = TRUE) %>% 
  st_transform(2248)

```

```{r read in mma results}

score_summary <- read_csv("K:/Models/MDOT_MMA/Chapter30_Scoring/Ch30_2023/MMA_scores/summarise/summarized_scores.csv")

zones <- st_read("K:\\Models\\MDOT_MMA\\Chapter30_Scoring\\Ch30_2023\\Land_use\\Lvl_2_Zones_12192017.shp", 
                 quiet = T) %>% 
  dplyr::select(LVL_2_NEW, ACRES, FIPS, COUNTY, MD_REGION) %>% 
  st_transform(2248) %>% 
  ms_simplify(keep = 0.2) %>% 
  st_make_valid()

score_summary_sf <- left_join(zones, score_summary,
                              by = c("LVL_2_NEW" = "origin")) %>% 
  filter(study_zone == "yes")

study_area_boundary <- ms_dissolve(filter(score_summary_sf, study_zone == "yes")) %>% 
  nngeo::st_remove_holes(.) %>% 
  st_make_valid()

```

## Extent of Study Area
The project study area is based on travel time to the zones in which the project is implemented – any zones within 45 minutes by transit (in the project build scenario) are part of the study area as are any zones within 15 minutes by driving (based on MSTM highway skims).


**Figure 11. Project Study Area Counties**
```{r study area map}

md_counties <- counties(state = "MD", cb = T,
                        progress_bar = FALSE) %>% 
  st_transform(2248) %>% 
  dplyr::select(NAME) %>% 
  rename(county = NAME) %>% 
  st_make_valid()

study_area_analysis <- ms_dissolve(filter(score_summary_sf, study_zone == "yes")) %>% 
  st_make_valid() %>% 
  select(-rmapshaperid) %>% 
  st_intersection(md_counties) %>% 
  mutate(sq_miles = as.numeric(st_area(.))/27878400) %>% 
  nngeo::st_remove_holes(.) %>% 
  st_make_valid()

tmap_mode("view")

pal <- rpg_color_pal("rpg_rainbow_no_grey")(5)
sf_use_s2(FALSE)
tm_shape(study_area_analysis) +
tm_borders(col = "#8400a8", lwd = 1.5) + tm_fill(alpha = 0.6, 
                                                 col = "county",
                                                 palette = pal) +
tm_shape(stops) + tm_dots(col = "white") +
tm_add_legend(type = "fill", col  = "#8400a8", 
              labels = "Study Area Boundary") +
tm_basemap ("Esri.WorldStreetMap")


```
**Table 6. Project Study Area Counties**

```{r study area table}
study_area_analysis %>% 
  st_drop_geometry() %>% 
adorn_totals(where = "row", fill = "-", na.rm = TRUE, name = "Total") %>%
kbl(col.names = c("County", "Sq. Miles in Study Area"), digits = 2) %>%
    kable_paper("hover", full_width = F)

```


## Travel Time Contours to Project
The service area analysis shows that Project 24-29 brings more of the study area within a one-hour travel time by transit.

## MMA Results

**Figure 12-13. No-Build and Build Jobs Accessibility in the Study Area**

```{r base and build mma mapping}

pal <- rpg_color_pal("rpg_colors")(17)

breaks <- classIntervals(score_summary_sf$build, 17, style = "jenks") 

nobuild_map <- tm_shape(score_summary_sf) +
tm_polygons("nobuild", 
            title = "Base Accessibility to Jobs", 
            palette = pal, style = "fixed",
            breaks = breaks$brks,
            lwd = 0.5, alpha = 0.9, 
            id = "change", textNA = "NA") +
tm_shape(study_area_boundary) +
tm_borders(col = "#8400a8", lwd = 1.5) +
tm_add_legend(type = "fill", col  = "#8400a8", 
              labels = "Study Area Boundary") +
tm_shape(stops) +
tm_dots(col = "#58585B", id = "stop_name", 
        popup.vars = "stop_name", 
        labels = "Project Stops", scale = 1,
        border.col = "white") +
tm_basemap ("Esri.WorldGrayCanvas")

build_map <- tm_shape(score_summary_sf) +
tm_polygons("build", 
            title = "Build Accessibility to Jobs", 
            style = "fixed", palette = pal,
            breaks = breaks$brks,
            lwd = 0.5, alpha = 0.9, 
            id = "change", textNA = "NA") +
tm_shape(study_area_boundary) +
tm_borders(col = "#8400a8", lwd = 1.5) +
tm_add_legend(type = "fill", col  = "#8400a8", 
              labels = "Study Area Boundary") +
tm_shape(stops) +
tm_dots(col = "#58585B", id = "stop_name", 
        popup.vars = "stop_name", 
        labels = "Project Stops", scale = 1,
        border.col = "white") +
tm_basemap ("Esri.WorldGrayCanvas")

tmap_arrange(nobuild_map, build_map, sync = T, ncol = 1)

```
